Predicting Tags for StackOverflow Posts

### 2013-06-20 stackExchange/writeups/iccm-2013/writeup.tex
foo
Former-commit-id: 8a9221c45f421ecd2730032b92d7d9e20ffbbfde [formerly d8f3480fb10c27f4d2603a125c047231ebf142ac]
Former-commit-id: 38ce017e476ea3b48c45d732fb45470970b3b14f

ACT-R's declarative memory retrieval process makes up the core of the StackOverflow model.
This is a more constrained and cognitively-plausible model than the set of general machine learning techniques used by \citeA{Kuo2011} for the same task. 
Interestingly, when using ACT-R's retrieval mechanism, the model performs significantly better than the less constrained models in \citeA{Kuo2011}.
So there is no reason to think that people do not engage in a process much like this to select tags.
However, more research is necessary before making the strong claim that the StackOverflow model \emph{is} the process people go through when selecting tags on the site, or tags in general.
In particular, the tag errors made by authors should be looked at, and model behavior should be tested against these important counter examples.
Also, places where the StackOverflow model deviates from ACT-R's default retrieval theory (i.e., the offset term, entropy and attentional weighting) should be looked at in greater detail.

>>>>

ACT-R's declarative memory retrieval process makes up the core of the StackOverflow model.
This is a more constrained and cognitively-plausible model than the set of general machine learning techniques used by \citeA{Kuo2011} for the same task. 
Interestingly, when using ACT-R's retrieval mechanism, the model performs significantly better than the less constrained models in \citeA{Kuo2011}.
So there is no reason to think that people do not engage in a process much like this to select tags.
However, more research is necessary before making the strong claim that the StackOverflow model \emph{is} the process people go through when selecting tags on the site, or tags in general.
In particular, the tag errors made by authors should be analyzed, and model behavior should be tested against these important counter examples.
Also, places where the StackOverflow model deviates from ACT-R's default retrieval theory (i.e., the offset term, entropy and attentional weighting) should be examined in greater detail.
